---
title: "flat_core.Rmd Core Functions"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.
-->

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# sort_uniq

Here are a few functions that I am creating as shorthands for some of commonly used
expressions/combined functions I keep coming back to. The idea is to read this package
and its functions into any random project I'm working on so I can have these
shorthands, handy (even if they don't seem very R-like).

```{r function-sort_uniq}
#' sort_uniq
#' 
#' Description
#' 
#' A Shorthand for unique() %>% sort()
#'
#' @param vec A vector that can be reasonably sorted
#' @return A sorted vector of unique values in the vector
#' @export
#'
#' @examples
sort_uniq <- function(vec) {
  sort(unique(vec))
}
```

```{r examples-sort_uniq}
vec <- sample(1:10, size = 20, replace=TRUE)

vec

sort_uniq(vec)
```

```{r tests-sort_uniq}
test_that("sort_uniq only returns 10 numbers", {
  expect_equal(
    object = {
      vec <- sample(1:10, size = 100, replace=TRUE)

      sort_uniq(vec)
    },

    expected = 1:10
  )
})
```

A funny thing I ended up realizing when trying to write a "simple test":

There's a tiny probability that this could fail randomly and it wouldn't even be wrong! So the lesson here is don't write tests like mine.

# len_uniq
    
```{r function-len_uniq}
#' len_uniq
#' 
#' A short hand for unique() %>% length()
#' 
#' @param vec A vector with a various objects
#' @return The number of unique objects in the vector
#' @export
#'
#' @examples
len_uniq <- function(vec) {
  length(unique(vec))
}
```
  
```{r example-len_uniq}
vec <- sample(1:10, size = 20, replace=TRUE)

vec

sort_uniq(vec)
```
  
```{r tests-len_uniq}
test_that("sort_uniq works", {
  expect_equal(
    object = {
      vec <- sample(1:10, size = 100, replace=TRUE)

      len_uniq(vec)
    },

    expected = 10
  )
})
```
  

# not_in

And finally, an actually personally irritating one of mine: NOT %in%. The fact that we can't
put in a `!%in%` or `not %in%` like in Python is one example where I can
actually say Python did it better than R here.

```{r function-not_in}
#' %!in%
#' 
#' An operator that negates the %in% operator
#' 
#' @return boolean
#' 
#' @export
`%!in%` <- Negate(`%in%`)
```
  
```{r example-not_in}
#' \dontrun{
#'     not_in(1, 2:10)
#' }
```
  

```{r tests-not_in, eval=FALSE}
test_that("`%!in%` works", {
  expect_true({
    1 %!in% 2:10
  }) 
})
```
  

```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_core.Rmd", vignette_name = "Core Functions")
```
